---
title: "Report and Cite Packages"
output: 
  rmarkdown::html_vignette:
    toc: true
    fig_width: 10.08
    fig_height: 6
tags: [r, report]
vignette: >
  %\VignetteIndexEntry{Report and Cite Packages}
  \usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  warning = FALSE,
  comment = "#"
)

options(
  knitr.kable.NA = "",
  width = 60
)

if (!requireNamespace("dplyr", quietly = TRUE)) {
  knitr::opts_chunk$set(eval = FALSE)
}
```

**Citing the packages, modules and software** you used for your analysis is
important to acknowledge the time and effort spent by people who create theses
tools (sometimes in their free-time, or at the expense of their own research),
but also for **reproducibility**. Indeed, statistical routines are often
implemented in different ways by different packages, which can lead to possible
discrepancies in the results. Explicitly mentioning that *"I did this using this function from that package version 1.2.3"* is a way of **protecting yourself** by being transparent about what you have found doing what you have
done.

But, understandably, you must have a lot of questions- 

> **That's great, but how to *actually* cite them?**

> **I used about 100 packages, should I cite them *all*?**

> **How should I report the system (the OS, the R version, etc.)?**

We attempt to answer these questions below :)

## What should I cite?

Ideally, you should indeed cite all the packages that you used. However, it's
often not possible to cite them all in the manuscript body. Therefore, we would
recommend the following guidelines:

### 1. Cite the main/important packages in the manuscript

This should be done for the packages that were central to your specific study
(*i.e.,* that got you the results that you reported) rather than data
manipulation tools (even though these are as much, if not *more*, important).
For example:

> Statistical analysis were carried out using R 4.1.0 (R Core Team, 2021), the
*rstanarm* (*v2.13.1*; Gabry \& Goodrich, 2016) and the *report* (*v0.2.0*;
Makowski, Patil, \& Lüdecke, 2019) packages. The full reproducible code is available in **Supplementary Materials**.

### 2. Present everything in Supplementary Materials

Then, in *Supplementary Materials*, you can show all the packages and functions
you used. To do it quickly, explicitly and in a reproducible fashion, we
recommend writing the *Supplementary Materials* with [**R Markdown**](https://rmarkdown.rstudio.com/), which can generate *docs* and *pdf*
files that you can submit along with your manuscript. Moreover, if you're using
R, you can include (usually at the end) every used package's citation using the
`cite_packages()` function from the
[**report**](https://github.com/easystats/report) package. For example:

```{r, results='asis'}
library(report)
library(dplyr)

cite_packages()
```

## Where 

Finding the right citation information is sometimes complicated. In `R`, this process is made quite easy, you simply run `citation("packagename")`. For instance, `citation("bayestestR")`:

    To cite bayestestR in publications use:

      Makowski, D., Ben-Shachar, M., \& Lüdecke, D. (2019). bayestestR:
      Describing Effects and their Uncertainty, Existence and Significance
      within the Bayesian Framework. Journal of Open Source Software,
      4(40), 1541. doi:10.21105/joss.01541
  
    A BibTeX entry for LaTeX users is
  
      @Article{,
        title = {bayestestR: Describing Effects and their Uncertainty, Existence and Significance within the Bayesian Framework.},
        author = {Dominique Makowski and Mattan S. Ben-Shachar and Daniel Lüdecke},
        journal = {Journal of Open Source Software},
        doi = {10.21105/joss.01541},
        year = {2019},
        number = {40},
        volume = {4},
        pages = {1541},
        url = {https://joss.theoj.org/papers/10.21105/joss.01541},
      }

For other languages, such as `Python` or `Julia`, it might be a little trickier,
but a quick search on Google (or github) should provide you with all the
necessary information (version, authors and date). 

**Keep in mind that it's better to have a slightly incomplete citation than no citation at all.**

## cite_easystats()

If you want to cite the **easystats** ecosystem, you can use the [`cite_easystats()`](https://easystats.github.io/report/reference/cite_easystats.html) function:

```{r results='asis'}
cite_easystats()
```
