---
title: "Get Started"
output: 
  rmarkdown::html_vignette:
    toc: true
    fig_width: 10.08
    fig_height: 6
tags: [r, report]
vignette: >
  %\VignetteIndexEntry{Get Started}
  \usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  tidy.opts = list(width.cutoff = 60),
  tidy = TRUE
)

options(
  knitr.kable.NA = "",
  digits = 4,
  width = 60
)

if (!requireNamespace("dplyr", quietly = TRUE)) {
  knitr::opts_chunk$set(eval = FALSE)
}
```

## Installation

First, install R and R studio. Then, copy and paste the following lines in the
console:

```{r eval=FALSE, message=FALSE, warning=FALSE}
install.packages("remotes")
remotes::install_github("easystats/report") # You only need to do that once
```

```{r message=FALSE, warning=FALSE}
library("report") # Load the package every time you start R
```

Great! The `report` package is now installed and loaded in your session.

## Examples

The `report` package works in a two step fashion. First, you create a `report`
object with the `report()` function. Then, this report object can be displayed
either textually (the default output) or as a table, using `as.data.frame()`.
Moreover, you can also access a more compact version of the report using
`summary()` on the report object.

**TO BE COMPLETED**.


<!-- ## Supported Objects -->

<!-- ### Dataframes -->

<!-- ```{r message=FALSE, warning=FALSE, eval=FALSE} -->
<!-- r <- report(iris) -->
<!-- text_short(r) -->
<!-- ``` -->
<!-- ```{r message=FALSE, warning=FALSE} -->
<!-- r <- report(iris) -->
<!-- print(text_short(r), width = 100) -->
<!-- ``` -->
<!-- ```{r message=FALSE, warning=FALSE} -->
<!-- table_short(r) -->
<!-- ``` -->


<!-- ### Grouped Dataframes -->

<!-- ```{r message=FALSE, warning=FALSE, eval=FALSE} -->
<!-- library(dplyr) -->

<!-- r <- iris %>%  -->
<!--   group_by(Species) %>%  -->
<!--   report(median = TRUE, range = FALSE)  # Display only the Median and MAD -->

<!-- text_short(r) -->
<!-- ``` -->
<!-- ```{r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- library(dplyr) -->

<!-- r <- iris %>%  -->
<!--   group_by(Species) %>%  -->
<!--   report(median = TRUE, range = FALSE)  # Display only the Median and MAD -->
<!-- print(text_short(r), width=100) -->
<!-- ``` -->
<!-- ```{r message=FALSE, warning=FALSE, eval=TRUE} -->
<!-- table_long(r) -->
<!-- ``` -->


<!-- ### Correlations and t-tests -->

<!-- ```{r message=FALSE, warning=FALSE, eval=FALSE} -->
<!-- report(cor.test(iris$Sepal.Length, iris$Petal.Length)) -->
<!-- ``` -->
<!-- ```{r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- print(report(cor.test(iris$Sepal.Length, iris$Petal.Length)), width = 100) -->
<!-- ``` -->

<!-- ```{r message=FALSE, warning=FALSE, eval=FALSE} -->
<!-- report(t.test(iris$Sepal.Length, iris$Petal.Length)) -->
<!-- ``` -->
<!-- ```{r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- print(report(t.test(iris$Sepal.Length, iris$Petal.Length)), width = 100) -->
<!-- ``` -->

<!-- ### Linear Models (LMs) -->

<!-- ```{r message=FALSE, warning=FALSE, eval=FALSE} -->
<!-- model <- lm(Sepal.Length ~ Petal.Length + Species, data=iris) -->
<!-- r <- report(model) -->

<!-- text_short(r) -->
<!-- ``` -->
<!-- ```{r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- model <- lm(Sepal.Length ~ Petal.Length + Species, data = iris)  -->
<!-- r <- report(model) -->

<!-- print(text_short(r), width = 100) -->
<!-- ``` -->

<!-- ```{r message=FALSE, warning=FALSE, eval=TRUE} -->
<!-- table_short(r) -->
<!-- ``` -->




<!-- ### General Linear Models (GLMs) -->

<!-- ```{r message=FALSE, warning=FALSE, eval=FALSE} -->
<!-- model <- glm(vs ~ mpg + cyl, data=mtcars, family="binomial") -->
<!-- r <- report(model) -->

<!-- text_long(r) -->
<!-- ``` -->
<!-- ```{r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- model <- glm(vs ~ mpg + cyl, data = mtcars, family = "binomial") -->
<!-- r <- report(model) -->

<!-- print(text_long(r), width = 100) -->
<!-- ``` -->

<!-- ```{r message=FALSE, warning=FALSE, eval=TRUE} -->
<!-- table_long(r) -->
<!-- ``` -->
