---
title: "report"
output: 
  github_document:
    toc: true
    fig_width: 10.08
    fig_height: 6
  rmarkdown::html_vignette:
    toc: true
    fig_width: 10.08
    fig_height: 6
tags: [r, report]
vignette: >
  \usepackage[utf8]{inputenc}
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  tidy.opts=list(width.cutoff=60),
  tidy=TRUE,
  fig.path = "README-"
)
options(knitr.kable.NA = '',
        digits = 4,
        width=60)
```


## Installation


Run the following:

```{r eval=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
install.packages("devtools")
devtools::install_github("neuropsychology/report")
```
```{r message=FALSE, warning=FALSE}
library("report")
```


## General Workflow

The `report` package works in a two steps fashion. First, creating a `report` object with the `report()` function (which takes different arguments depending on the type of object you are reporting). Then, this report can be displayed either textually, using `to_text()`, or as a table, using `to_table()`. Moreover, you can also access a more detailed (but less digest) version of the report using `to_fulltext()` and `to_fulltable()`. Finally, the `values()` makes it easy to access all the internals of a model. 



## Examples


### Dataframes

```{r message=FALSE, warning=FALSE, eval=FALSE}
report(iris)
```
```{r message=FALSE, warning=FALSE}
print(report(iris), width=100)
```

The reports nicely work within the *tidyverse*:

```{r message=FALSE, warning=FALSE, eval=FALSE}
library(dplyr)

iris %>% 
  group_by(Species) %>% 
  report(median = TRUE, range = FALSE)  # Display only the Median and MAD
```
```{r message=FALSE, warning=FALSE}
library(dplyr)

iris %>% 
  group_by(Species) %>% 
  report(median = TRUE, range = FALSE) %>% 
  print(width=100)
```


### Correlations and t-tests

```{r message=FALSE, warning=FALSE, eval=FALSE}
report(cor.test(iris$Sepal.Length, iris$Petal.Length))
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
print(report(cor.test(iris$Sepal.Length, iris$Petal.Length)), width=100)
```

```{r message=FALSE, warning=FALSE, eval=FALSE}
report(t.test(iris$Sepal.Length, iris$Petal.Length))
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
print(report(t.test(iris$Sepal.Length, iris$Petal.Length)), width=100)
```
### Linear Models (LM)

The difference between regular and full reports becomes obvious for more complicated models.

```{r message=FALSE, warning=FALSE, eval=FALSE}
model <- lm(Sepal.Length ~ Petal.Length + Species, data=iris)
r <- report(model)

to_text(r)
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
model <- lm(Sepal.Length ~ Petal.Length + Species, data=iris) 
r <- report(model)

to_text(r, width=100)
```


```{r message=FALSE, warning=FALSE, eval=FALSE}
to_fulltext(r)
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
to_fulltext(r, width=100)
```

```{r message=FALSE, warning=FALSE, eval=FALSE}
to_table(r, digits=2)
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(to_table(r, digits=2))
```

```{r message=FALSE, warning=FALSE, eval=FALSE}
to_fulltable(r, digits=2)
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(to_fulltable(r, digits=2))
```

