---
title: "Get Started"
output: 
  github_document:
    toc: true
    fig_width: 10.08
    fig_height: 6
  rmarkdown::html_vignette:
    toc: true
    fig_width: 10.08
    fig_height: 6
tags: [r, report]
vignette: >
  \usepackage[utf8]{inputenc}
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  tidy.opts = list(width.cutoff = 60),
  tidy = TRUE,
  fig.path = "README-"
)
options(knitr.kable.NA = '',
        digits = 4,
        width = 60)
if (!requireNamespace("dplyr", quietly = TRUE)) {
  knitr::opts_chunk$set(eval = FALSE)
}
```


## Installation

First, install R. Then, run the following in the console:

```{r eval=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
install.packages("devtools")
devtools::install_github("neuropsychology/report")
```
```{r message=FALSE, warning=FALSE}
library("report")
```


## Functions


The `report` package works in a two steps fashion. First, creating a `report` object with the `report()` function (which takes different arguments depending on the type of object you are reporting). Then, this report can be displayed either textually, using `text_short()`, or as a table, using `table_short()`. Moreover, you can also access a more detailed (but less digest) version of the report using `text_long()` and `table_long()`.


## Supported Objects

### Dataframes

```{r message=FALSE, warning=FALSE, eval=FALSE}
r <- report(iris)
text_short(r)
```
```{r message=FALSE, warning=FALSE}
r <- report(iris)
print(text_short(r), width = 100)
```
```{r message=FALSE, warning=FALSE}
table_short(r)
```


### Grouped Dataframes

```{r message=FALSE, warning=FALSE, eval=FALSE}
library(dplyr)

r <- iris %>% 
  group_by(Species) %>% 
  report(median = TRUE, range = FALSE)  # Display only the Median and MAD

text_short(r)
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)

r <- iris %>% 
  group_by(Species) %>% 
  report(median = TRUE, range = FALSE)  # Display only the Median and MAD
print(text_short(r), width=100)
```
```{r message=FALSE, warning=FALSE, eval=TRUE}
table_long(r)
```


### Correlations and t-tests

```{r message=FALSE, warning=FALSE, eval=FALSE}
report(cor.test(iris$Sepal.Length, iris$Petal.Length))
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
print(report(cor.test(iris$Sepal.Length, iris$Petal.Length)), width = 100)
```

```{r message=FALSE, warning=FALSE, eval=FALSE}
report(t.test(iris$Sepal.Length, iris$Petal.Length))
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
print(report(t.test(iris$Sepal.Length, iris$Petal.Length)), width = 100)
```

### Linear Models (LMs)

```{r message=FALSE, warning=FALSE, eval=FALSE}
model <- lm(Sepal.Length ~ Petal.Length + Species, data=iris)
r <- report(model)

text_short(r)
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
model <- lm(Sepal.Length ~ Petal.Length + Species, data = iris) 
r <- report(model)

print(text_short(r), width = 100)
```

```{r message=FALSE, warning=FALSE, eval=TRUE}
table_short(r)
```




### General Linear Models (GLMs)

```{r message=FALSE, warning=FALSE, eval=FALSE}
model <- glm(vs ~ mpg + cyl, data=mtcars, family="binomial")
r <- report(model)

text_long(r)
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
model <- glm(vs ~ mpg + cyl, data = mtcars, family = "binomial")
r <- report(model)

print(text_long(r), width = 100)
```

```{r message=FALSE, warning=FALSE, eval=TRUE}
table_long(r)
```
