---
title: "Publication-ready Tables"
output: 
  rmarkdown::html_vignette:
    toc: true
    fig_width: 10.08
    fig_height: 6
tags: [r, report]
vignette: >
  %\VignetteIndexEntry{Publication-ready Tables}
  \usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  warning = FALSE,
  comment = "#"
)

options(
  knitr.kable.NA = "",
  width = 60
)

if (!requireNamespace("dplyr", quietly = TRUE)) {
  knitr::opts_chunk$set(eval = FALSE)
}
```


First, load the `{report}` package, part of the `{easystats}` collection.

```{r}
library(easystats)
```


## Getting started with correlations

Let's start by demonstrating some features with simple tests. The function `report_table()` can be used to create a table for many R objects.

```{r}
results <- cor.test(mtcars$mpg, mtcars$wt)

report_table(results)
```

We can also obtain a shorter version by running `summary()` on the output (that we are going to store in a variable called `t` - like table)

```{r}
t <- summary(report_table(results))
t
```

In the example above, running just `t` ran `print(t)` under the hood, which prints the table inside the console. However, one can nicely display that table in markdown documents using `display()`.

```{r, results='asis'}
display(t)
```

We can further customize this table, by adding significance stars, 


```{r, results='asis'}
display(t, 
        stars = TRUE,
        title = "Table 1", 
        footer = "Correlation in the mtcars (n = 32) dataset.\n*** p < .001")
```

## *t*-tests, ...

```{r}
results <- t.test(mpg ~ am, data=mtcars)

t <- report_table(results)
t
```



## Regression Models

```{r}
model <- lm(Petal.Length ~ Species * Petal.Width, data = iris)

report_table(model)
```


