---
title: "report: Automated Reporting of Results and Statistical Models in R"
tags:
  - R
  - easystats
authors:
- affiliation: 1
  name: Dominique Makowski
  orcid: 0000-0001-5375-9967
- affiliation: 2
  name: Indrajeet Patil
  orcid: 0000-0003-1995-6531
- affiliation: 3
  name: Mattan S. Ben-Shachar
  orcid: 0000-0002-4287-4801
- affiliation: 4
  name: Brenton M. Wiernik^[Brenton Wiernik is currently an independent researcher and Research Scientist at Meta, Demography and Survey Science. The current work was done in an independent capacity.]
  orcid: 0000-0001-9560-6336
- affiliation: 5
  name: Etienne Bacher
  orcid: 0000-0002-9271-5075 
- affiliation: 6
  name: Daniel Lüdecke
  orcid: 0000-0002-8895-3206
- affiliation: 7
  name: Rémi Thériault
  orcid: 0000-0003-4315-6788
    
affiliations:
- index: 1
  name: Nanyang Technological University, Singapore
- index: 2
  name: Center for Humans and Machines, Max Planck Institute for Human Development, Berlin, Germany
- index: 3
  name: Ben-Gurion University of the Negev, Israel
- index: 4
  name: Independent Researcher
- index: 5
  name: Luxembourg Institute of Socio-Economic Research (LISER), Luxembourg
- index: 6
  name: University Medical Center Hamburg-Eppendorf, Germany
- index: 7
  name: Université du Québec à Montréal, Montréal, Canada
      
date: "`r Sys.Date()`"
bibliography: paper.bib
output: rticles::joss_article
csl: apa.csl
journal: JOSS
link-citations: yes
---

```{r, warning=FALSE, message=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  out.width = "100%",
  dpi = 300,
  comment = "#>",
  message = FALSE,
  warning = FALSE
)

options(width = 60)

library(report)
set.seed(2016)
```

# Summary

The `{report}` package is a powerful tool for researchers who use R to analyze data and create reports for publication. It bridges the gap between R's output and the formatted results to be included in a manuscript, allowing users to easily convert statistical models and data frames into textual reports that are suitable for publication. This paper provides an overview of this package, including its features, advantages, and how to use it. We also provide examples of how the package can be used to standardize and improve results reporting in R.

# Statement of Need

Reporting results is a crucial part of scientific research. Researchers need to ensure that their results are reported accurately and clearly, so that other researchers can understand and reproduce their work. However, the process of results reporting can be time-consuming and error-prone, particularly when it comes to formatting data for publication. The `{report}` package was developed to address this problem, providing researchers with a tool that can help standardize and improve reporting results from their workflows in R.

# Features

The package includes several features that make it a valuable tool for researchers. It can convert statistical models and data frames into textual reports, which can be easily customized and formatted to meet the requirements of a particular journal or publication. The package supports a wide range of output formats, including HTML, LaTeX, and Microsoft Word, via RMarkdown.

Using this package in an analytic workflow has several advantages. First, it can help standardize results reporting across a research team or project, ensuring that everyone is using the same format and style. Second, the package can save researchers time by automating many of the tasks involved in reporting results, such as formatting tables and text. Third, the package can improve the quality of results reporting by providing users with a tool that is specifically designed for this purpose. Additionally, it prevents any copy-and-paste errors.

The examples below illustrate the ease with which `{report}` can create detailed textual or tabular summaries for statistical objects:

```{r}
library(report)

m_lm <- lm(mpg ~ qsec + wt, data = mtcars)
report(m_lm)

library(lme4)
m_lmer <- lmer(Sepal.Length ~ Petal.Length + (1 | Species), data = iris)
report(m_lmer)

library(rstanarm)
m_rstan <- stan_glm(mpg ~ qsec + wt, data = mtcars, refresh = 0, iter = 1000)
report(m_rstan)
```

You can also seamlessly integrate `{report}` with *tidyverse* workflows:

```{r, warning=FALSE}
library(dplyr)

iris %>%
  select(-starts_with("Sepal")) %>%
  group_by(Species) %>%
  report() %>%
  summary()
```

# Conclusion

The `{report}` package is a valuable tool for researchers who use R to analyze data and create reports for publication. It can help standardize and improve results reporting while saving researchers time and improving the quality of their work. 

# Licensing and Availability

`{report}` is licensed under the GNU General Public License (v3.0), with all source code openly developed and stored on GitHub (<https://github.com/easystats/report>), along with a corresponding issue tracker for bug reporting and feature enhancements. In the spirit of honest and open science, we encourage requests, tips for fixes, feature updates, as well as general questions and concerns via direct interaction with contributors and developers.

# Acknowledgments

`{report}` is part of the collaborative [*easystats*](https://easystats.github.io/easystats/) ecosystem. Thus, we thank the [members of easystats](https://github.com/orgs/easystats/people) as well as the users.

# References
